### 2023-03-14 main.tex
G-check

We make the following ansatz for the eigevectors of the diagonal-triangular spin chain:

@@

|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

@@

&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\mathbbm{1}_{\{k_{2}+k_{3}\neq 0\}}\Delta^{k_{2}+k_{3}}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

\Delta^{m_{2}+m_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2}+m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

T_{0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}&G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}\\&=\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0

@@

@@

conditions \eqref{condition1} and \eqref{condition2} are easilly satisfied. To fulfill condition \eqref{condition3}% we can think about $m_{1}:=L-m_{2}-m_{3}$ as the number of empty states in the whole chain. We can further introducte $m:=m_{2}+m_{3}$ and then write $m_{1}=L-m$. Therefore we have an invertivle map between holes and particles, therefore we can think about $\left(B_{2}(x)+B_{3}(x)\right)$ as a lowering operator and 
We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries. For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

For $i\neq 1$ we have
\begin{equation}
\begin{split}
 \sum_{i,j=2}^N [E_{ij}E_{ji},E_{k1}]&=\sum_{i,j=2}^N E_{ij} [E_{ji},E_{k1}]+\sum_{i,j=2}^N  [E_{ij},E_{k1}]E_{ji}=\sum_{j=2}^N( E_{kj} E_{j1}+ E_{j1} E_{kj})
\\&=\sum_{j=2}^N( 2E_{kj} E_{j1}+ [E_{j1}, E_{kj}])=2\sum_{j=2}^N E_{kj} E_{j1}-(N-1)E_{k1}
 \end{split}
\end{equation}

>>>>

We make the following ansatz for the eigevectors of the diagonal-triangular spin chain. Consider the whole chain of dimension $L$. Then, $m=m_{2}+m_{3}$ sites have particles of a type $2$ or $3$ and the remaining $L-m$ are empty. For fixed $m$ there is a one to one correspondence between empty and occupeid sites. Therefore, our ansatz is that $\forall m\in \{0,\ldots,L\}$ 

@@

|\Psi_{L-m}^{\Delta}\rangle=\mathbbm{1}_{\{m_{2}+m_{3}=m\}}\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}

@@

T_{\Delta}(x)|\Psi_{L-m}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{L-m}^{\Delta}\rangle

@@

&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}

@@

\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}

@@

\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}

@@

&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{L-m}^{0}\rangle|_{\epsilon=0}

@@

\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\mathbbm{1}_{\{k_{2}+k_{3}\neq 0\}}\Delta^{k_{2}+k_{3}}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}-1}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}

@@

\Delta^{m_{2}+m_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2}+m_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}

@@

T_{0}(x)|\Psi_{m_{2},m_{3}}^{0}|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}

@@

\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}&G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}\\&=\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}

@@

\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2},m_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}=0

@@

\begin{equation}\label{G-solution}

@@

conditions \eqref{condition1} and \eqref{condition2} are easilly satisfied. To fulfill condition \eqref{condition3} we observe that, under the condition that $m=m_{2}+m_{3}$ we have that the action of \eqref{G-solution} on $|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}$ leads to a completely occupied state (with both species $2$ and $3$). Therefore, applying to it the rising operator$\left(B_{2}(x)+B_{3}(x)\right)$ we obtain zero.

{\color{blue}We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries. For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
\begin{equation}
|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\end{equation}

@@

}
For $i\neq 1$ we have
 \sum_{i,j=2}^N [E_{ij}E_{ji},E_{k1}]&=\sum_{i,j=2}^N E_{ij} [E_{ji},E_{k1}]+\sum_{i,j=2}^N  [E_{ij},E_{k1}]E_{ji}=\sum_{j=2}^N( E_{kj} E_{j1}+ E_{j1} E_{kj})
\\&=\sum_{j=2}^N( 2E_{kj} E_{j1}+ [E_{j1}, E_{kj}])=2\sum_{j=2}^N E_{kj} E_{j1}-(N-1)E_{k1}
